Evaluation

### 2018-06-29 evaluation.Rmd

**RMSE**: Root mean square error, this is a metric used to evaluate the point estimate of a forecast.  
**Coverage**: This is the percentage of observations which fell within the `r 100 * pred_interval`% confidence interval of a forecast. Ideally this would be equal to `r pred_interval`. If it's higher than `r pred_interval` the forecasts intervals are too wide, if it's lower then the forecast intervals are too narrow.

>>>>

**RMSE**: Root mean square error, this is a metric used to evaluate the point estimate of a forecast.  
**Coverage**: This is the percentage of observations which fell within the 90% confidence interval of a forecast. Ideally this would be equal to 0.90. If it is higher than 0.90 the forecasts intervals are too wide, if it's lower then the forecast intervals are too narrow.
